Local simple connectedness of boundaries of hyperbolic groups

### 2020-03-10 paper.tex
Spellcheck

  Let $\alpha'$ be a bi-infinite geodesic with $\alpha'(-\infty) = \xi$ and
  $\alpha'(\infty) \in C$ and let $x' \in \alpha' \intersection H$. The ideal
  triangle with vertices $\xi$, $\alpha(\infty)$ and $\alpha'(\infty)$ is
  $\delta$-slim, so the subray of $\alpha$ between $\xi$ and $w$ is contained
  in a $\delta$-neighbourhood of $\alpha'$.  Let $w' \in \alpha'$ be a point
  with $\dist(w, w') \leq \delta$.

@@

\begin{proof}
  Suppose that a compact subset $C$ of $\boundary G - \set\xi$ is not contained
  in $U_i$ for infinitely many $i$. Then after passing to a subsequence there
  exists for each $i$ a point $\zeta_i \in C\setminus U_i$, so by
  Lemma~\ref{lem:describing_q_i} for each $i$ there is a geodesic ray
  $\alpha_i$ from $g_i$ to $\zeta_i$ that meets $N_{2\delta+1}^{g_i\cdot
  S_{n_i}}(g_i\cdot S_{n_i} - H_i)$. After passing to a subsequence, the rays
  $\alpha_i$ converge uniformly on compact subsets toa bi-infinite geodesic
  from $\xi$ to some pint $\zeta \in C$ that does not meet $H$, contradicting
  Lemma~\ref{lem:geodesicsmeethorosphere}.
\end{proof}

@@

\begin{proof}
  Let $B\subset H$ be a bounded set containing all points where geodesics with
  one limit point equal to $\xi$ and the other in $C$ meet $H$; this set exists
  by \cref{lem:boundedintersection}.

  Fix $\alpha$ to be some geodesic with $\alpha(-\infty)=\xi$ and
  $\alpha(\infty)\in C$ and let $x$ be a point of intersection between $\alpha$
  and $B$. Since the triangle with vertcies $x$, $g_i$ and $\xi$ is
  $\delta$-slim, and $\dist(x, [\xi, g_i]) \to \infty$ as $i\to\infty$, for
  each $i$ there exists a point $y_i$ on $[g_i, x]$ with $\dist(y_i, \alpha)
  \leq \delta$ and so that $y_i \to \xi$ as $i\to\infty$. Let $z_i \in \alpha$
  be such that $\dist(y_i, z_i)\leq\delta$.

@@

  Since $\dist(z_i', x') > 2\delta$, the distance from $y_i'$ to the subray of
  $\alpha'$ from $x'$ to $\zeta$ is greater than $\delta$. Therefore by
  considering a triangle with vertices $g_i$, $x'$ and $\zeta$ we see that
  there exists a point $w_i$ on a geodesic ray $\eta_i$ from $g_i$ to $\zeta$
  with $\dist(w_i, y_i') \leq \delta$. It follows that $\dist(w_i, z_i') \leq
  4\delta$, and we know that $\dist(x', z_i') > 5\delta$, so $\dist(x', [z_i',
  w_i]) > \delta$ and therefore $\dist(x', \eta_i) \leq \delta$.

@@

  Now, $g_i\cdot \zeta_1^i$ and $g_i\cdot\zeta_2^i$ map by $q_i$ to points in
  simplices adjacent to $x_1$ and $x_2$, so by Lemma~\ref{lem:propermaps} we
  can pass to a subsequence so that the sequences $g_i\cdot \zeta_1^i$ anl
  $g_i\cdot\zeta_2^i$ converge to points $\zeta_1$ and $\zeta_2$ in $\boundary
  G - \set\xi$ as $i \to \infty$.

@@

We can immediately give a sufficient condition for $\S_M$ to be satisfied. This
result is analagous to Proposition~\ref{prop:BM2}.

@@

  Fix a vertex $v$ of $\boundary\Delta$; then there exist group elements $g_i
  \in G$ such that $g_i\cdot f_i(v)$ is a fixed vertex of $K$. Pass to a
  subsequence as in Section~\ref{sec:horoball}, and to a deeper subsequence so
  that $g_i\cdot f_i(w)$ is independent of $i$ for all vertices $w \in \sd^M
  \boundary\Delta$. Then the map $g_i\composed f_i$ is independent of $i$; call
  this map $f$. It remains to show that $f$ is nullhomotopic in $H$; then it is
  nullhomotopic by an affine map by~\cite{zeeman64}, and this gives a
  contradiction for $i$ sufficiently large.

@@

Thrououghout the rest of this section we assume that $G$ satisfies
$\ddag'_M$ and $\S_M$ for all $M$.

@@

  Using $\ddag'_C$ we can extend $\gamma_0\disjointunion\gamma_1$ along $x
  \times [0,1]$ for each vertex $x$ of $J$ in such a way that the extension
  along each edge $x\times [0,1]$, when composed with $p^\infty_n$, admits a
  simplicial approximation connecting $f_0(x)$ to $f_1(x)$ after at most $L$
  subdivisions of the interval. Finally, using the condition $\S_?$, we deduce
  that $f_0 \disjointunion f_1$ admints an affine extension to $\sd^{L'}(J
  \times [0,1])$ after Call the extension $F$ and let $h = i^n_\infty \composed
  F$, so that $h$ is a homotopy from $i^n_\infty\composed f_0$ to
  $i^n_\infty\composed f_1$.

@@

  Furthermore, $\dist(y, i^n_{n+1}(y))$ is bounded by $2\delta+1$, and
  $\newdist(i^n_{n+1}(y), i^n_{n+1}\composed p^\infty_n (\xi))$ is bounded by
  the product of $D$ and the the number of 2-simpices in $\sd^L\Delta$, where
  $L$ is the number appearing in Proposition~\ref{prop:i_in_dimension_2}.  By
  putting all this together we obtain a bound $C$ on
  $\newdist(i^n_{n+1}\composed p^\infty_n(\xi), p^\infty_{n+1}(\xi))$, and then
  $\dist(x_1, x_2) \leq C + 2D$.
\end{proof}

>>>>

  Let $\alpha'$ be a bi-infinite geodesic with $\alpha'(-\infty) = \xi$ and
  $\alpha'(\infty) \in C$ and let $x' \in \alpha' \intersection H$. The ideal
  triangle with vertices $\xi$, $\alpha(\infty)$ and $\alpha'(\infty)$ is
  $\delta$-slim, so the sub-ray of $\alpha$ between $\xi$ and $w$ is contained
  in a $\delta$-neighbourhood of $\alpha'$.  Let $w' \in \alpha'$ be a point
  with $\dist(w, w') \leq \delta$.

@@

\begin{proof}
  Suppose that a compact subset $C$ of $\boundary G - \set\xi$ is not contained
  in $U_i$ for infinitely many $i$. Then after passing to a subsequence there
  exists for each $i$ a point $\zeta_i \in C\setminus U_i$, so by
  Lemma~\ref{lem:describing_q_i} for each $i$ there is a geodesic ray
  $\alpha_i$ from $g_i$ to $\zeta_i$ that meets $N_{2\delta+1}^{g_i\cdot
  S_{n_i}}(g_i\cdot S_{n_i} - H_i)$. After passing to a subsequence, the rays
  $\alpha_i$ converge uniformly on compact subsets to a bi-infinite geodesic
  from $\xi$ to some pint $\zeta \in C$ that does not meet $H$, contradicting
  Lemma~\ref{lem:geodesicsmeethorosphere}.
\end{proof}

@@

\begin{proof}
  Let $B\subset H$ be a bounded set containing all points where geodesics with
  one limit point equal to $\xi$ and the other in $C$ meet $H$; this set exists
  by \cref{lem:bounded_intersection}.

  Fix $\alpha$ to be some geodesic with $\alpha(-\infty)=\xi$ and
  $\alpha(\infty)\in C$ and let $x$ be a point of intersection between $\alpha$
  and $B$. Since the triangle with vertices $x$, $g_i$ and $\xi$ is
  $\delta$-slim, and $\dist(x, [\xi, g_i]) \to \infty$ as $i\to\infty$, for
  each $i$ there exists a point $y_i$ on $[g_i, x]$ with $\dist(y_i, \alpha)
  \leq \delta$ and so that $y_i \to \xi$ as $i\to\infty$. Let $z_i \in \alpha$
  be such that $\dist(y_i, z_i)\leq\delta$.

@@

  Since $\dist(z_i', x') > 2\delta$, the distance from $y_i'$ to the sub-ray of
  $\alpha'$ from $x'$ to $\zeta$ is greater than $\delta$. Therefore by
  considering a triangle with vertices $g_i$, $x'$ and $\zeta$ we see that
  there exists a point $w_i$ on a geodesic ray $\eta_i$ from $g_i$ to $\zeta$
  with $\dist(w_i, y_i') \leq \delta$. It follows that $\dist(w_i, z_i') \leq
  4\delta$, and we know that $\dist(x', z_i') > 5\delta$, so $\dist(x', [z_i',
  w_i]) > \delta$ and therefore $\dist(x', \eta_i) \leq \delta$.

@@

  Now, $g_i\cdot \zeta_1^i$ and $g_i\cdot\zeta_2^i$ map by $q_i$ to points in
  simplices adjacent to $x_1$ and $x_2$, so by Lemma~\ref{lem:propermaps} we
  can pass to a subsequence so that the sequences $g_i\cdot \zeta_1^i$ and
  $g_i\cdot\zeta_2^i$ converge to points $\zeta_1$ and $\zeta_2$ in $\boundary
  G - \set\xi$ as $i \to \infty$.

@@

We can immediately give a sufficient condition for $\S_M$ to be satisfied. This
result is analogous to Proposition~\ref{prop:BM2}.

@@

  Fix a vertex $v$ of $\boundary\Delta$; then there exist group elements $g_i
  \in G$ such that $g_i\cdot f_i(v)$ is a fixed vertex of $K$. Pass to a
  subsequence as in Section~\ref{sec:horoball}, and to a deeper subsequence so
  that $g_i\cdot f_i(w)$ is independent of $i$ for all vertices $w \in \sd^M
  \boundary\Delta$. Then the map $g_i\composed f_i$ is independent of $i$; call
  this map $f$. It remains to show that $f$ is null-homotopic in $H$; then it is
  null-homotopic by an affine map by~\cite{zeeman64}, and this gives a
  contradiction for $i$ sufficiently large.

@@

Throughout the rest of this section we assume that $G$ satisfies
$\ddag'_M$ and $\S_M$ for all $M$.

@@

  Using $\ddag'_C$ we can extend $\gamma_0\disjointunion\gamma_1$ along $x
  \times [0,1]$ for each vertex $x$ of $J$ in such a way that the extension
  along each edge $x\times [0,1]$, when composed with $p^\infty_n$, admits a
  simplicial approximation connecting $f_0(x)$ to $f_1(x)$ after at most $L$
  subdivisions of the interval. Finally, using the condition $\S_?$, we deduce
  that $f_0 \disjointunion f_1$ admits an affine extension to $\sd^{L'}(J
  \times [0,1])$ after Call the extension $F$ and let $h = i^n_\infty \composed
  F$, so that $h$ is a homotopy from $i^n_\infty\composed f_0$ to
  $i^n_\infty\composed f_1$.

@@

  Furthermore, $\dist(y, i^n_{n+1}(y))$ is bounded by $2\delta+1$, and
  $\newdist(i^n_{n+1}(y), i^n_{n+1}\composed p^\infty_n (\xi))$ is bounded by
  the product of $D$ and the the number of 2-simplices in $\sd^L\Delta$, where
  $L$ is the number appearing in Proposition~\ref{prop:i_in_dimension_2}.  By
  putting all this together we obtain a bound $C$ on
  $\newdist(i^n_{n+1}\composed p^\infty_n(\xi), p^\infty_{n+1}(\xi))$, and then
  $\dist(x_1, x_2) \leq C + 2D$.
\end{proof}
